A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/summary.tex
compressed summary table

\begin{figure}[h]
\centering
\begin{tabular}{llcccccc}
\multicolumn{8}{c}{Number of Turkers per language}\\
\hline\hline
&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality}\\
&&&Overall&By country&In region&Out of region\\
\hline\hline
hi&Hindi&362&299&India (285) Uae (5) &\textbf{0.5395}&0.474\\
&&&&Uk (5) Other (5) &&&\\
&&&&&&&\\
ta&Tamil&304&278&India (271) US (3) &\textbf{0.5528}&0.54\\
&&&&Canada (2) Other (2) &&&\\
&&&&&&&\\
ml&Malayalam&284&235&India (224) Uae (6) &0.4759&\textbf{0.5523}\\
&&&&US (3) Other (2) &&&\\
&&&&&&&\\
es&Spanish&244&205&US (131) Mexico (18) &\textbf{0.2723}&0.2675\\
&&&&Westspain (14) Other (43) &&&\\
&&&&&&&\\
fr&French&217&183&India (68) US (48) &0.2907&\textbf{0.307}\\
&&&&France (25) Other (42) &&&\\
&&&&&&&\\
de&German&170&99&Germany (51) US (29) &\textbf{0.3529}&0.306\\
&&&&Austria (9) Other (11) &&&\\
&&&&&&&\\
it&Italian&166&98&Italy (44) US (32) &\textbf{0.3223}&0.2733\\
&&&&Romania (9) Other (13) &&&\\
&&&&&&&\\
zh&Chinese&151&123&US (80) Singapore (15) &\textbf{0.4171}&0.4123\\
&&&&China (14) Other (21) &&&\\
&&&&&&&\\
te&Telugu&137&102&India (98) US (3) &\textbf{0.4793}&0.4051\\
&&&&Uae (1) &&&\\
&&&&&&&\\
ms&Malay&131&15&Malaysia (8) Singapore (4) &\textbf{0.2964}&0.276\\
&&&&US (2) Other (1) &&&\\
&&&&&&&\\
\hline\hline
\end{tabular}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\begin{tabular}{lccc}
\multicolumn{4}{c}{Number of turkers per language}\\
\hline\hline
&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&In-region turker locations\\
&In region&Out of region\\
\hline\hline
Hindi&\textbf{0.54 (299)}&0.47 (63)&India (285) UAE (5) UK (5) Other (5) \\
Tamil&\textbf{0.55 (278)}&0.54 (26)&India (271) US (3) Canada (2) Other (2) \\
Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) Other (2) \\
Spanish&\textbf{0.27 (205)}&0.27 (39)&US (131) Mexico (18) Spain (14) Other (43) \\
French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) Other (42) \\
German&\textbf{0.35 (99)}&0.31 (71)&Germany (51) US (29) Austria (9) Other (11) \\
Italian&\textbf{0.32 (98)}&0.27 (68)&Italy (44) US (32) Romania (9) Other (13) \\
Chinese&\textbf{0.42 (123)}&0.41 (28)&US (80) Singapore (15) China (14) Other (21) \\
Telugu&\textbf{0.48 (102)}&0.41 (35)&India (98) US (3) UAE (1) \\
Malay&\textbf{0.30 (15)}&0.28 (116)&Malaysia (8) Singapore (4) US (2) Other (1) \\
\hline\hline
\end{tabular}
\end{figure}
